---
title: "Parameter Estimation"
author: "Pernille Brams & Klara Krøyer Fomsgaard"
date: "4/1/2024"
output:
    html_document:
    toc: true
editor_options: 
  chunk_output_type: console
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Setting the root directory
setwd("/Users/pernillebrams/Desktop/AARHUS_UNIVERSITY/kandidat/decision_making/decision_making/exam_pref_strat/DecMak_2023_PREFSTRAT/JANUARY")

# Clearing the environment
rm(list=ls())

```

## Setting up
```{r setup}
# Get libraries
library(pacman)

pacman::p_load(tidyverse,
               lme4,
               ggplot2,
               R2jags,
               brms,
               coda)

# Get in preprocessed data
# - Full data
GLMdata <- read.csv("data/preprocessed/GLMdata.csv")

# - Subset
DMdata <- read.csv("data/preprocessed/DMdata.csv")

# - Contributions
contributions <- read.csv("data/preprocessed/contributions.csv")

```

# 1. Get variables needed for modelling
We need
- ngroups
- ntrials
- groupSize
- Ga (avg contribution in the group without yourself)
- c (own contribution)

The script get_vars.R makes these for us.

First, let's get an overview: 
```{r get_vars}
# We have these cols
colnames(DMdata)

# Overview + sanity check
length(unique(DMdata$id)) # 192
length(unique(DMdata$idgroup)) # 64
length(unique(DMdata$sessionid)) # 8
length(unique(DMdata$period)) # 15
length(unique(DMdata$grouptype)) # 4
length(unique(DMdata$condition)) # 3
length(unique(DMdata$type)) # 4
length(unique(DMdata$subject)) # 24

max(unique(DMdata$sum_contribution_g)) # 60
summary(unique(DMdata$avg_contribution_g)) # 0-20
max(unique(DMdata$sum_contribution_g)) # 60

# Get vars from DMdata
source("scripts/get_vars.R")

# Define MPD for later usage
MPD <- function(x) {
  density(x)$x[which(density(x)$y==max(density(x)$y))]
}

```

# 2. Fit model
```{r fitting_jags}
# Define data list
data_list <- list(
  ngroups = ngroups,     # Should be 64
  ntrials = ntrials,     # Should be 15
  groupSize = groupSize, # Should be 3
  Ga = Ga,               # Should have dim(Ga) = 3 15 64
  c = c)                 # Should have dim(c) = 3 15 64

# Check dims
ngroups
ntrials
groupSize
dim(Ga)
dim(c)

# Define parameters of interest
params <- c("omega", "rho", "alpha")

# Run model
samples <- jags(data = data_list,
                inits=NULL,
                parameters.to.save = params,
                model.file ="modelling/parameter_estimation/CC_model_individual.txt", 
                n.chains = 3,
                n.iter=40000, n.burnin=8000, n.thin=1) #, n.cluster=3)

dim(samples$BUGSoutput$sims.list$alpha) #  96000     3    64
dim(samples$BUGSoutput$sims.list$rho)   #  96000     3    64

# posterior plot code put somewhere
# plot(density(rnorm(10000,0,1/sqrt(0.147))),ylim=c(0,.7),main="alpha")
# lines(density(Y$betaX_alpha),col="red")

```

# 3. Evaluate Model Fit (Convergence Diagnostics)
```{r make_mcmc}
# -- Convergence diagnostics
mcmc_samples <- as.mcmc(samples)
#saveRDS(samples, file = "samples.rds")
#saveRDS(mcmc_samples, file = "mcmc_samples.rds")

#summary(mcmc_samples) # takes long time to run
```

```{r gelman_diagnostic}
# --- Gelman Diagnostic for convergence (get multivariate PSRF)
gelman_diag <- gelman.diag(mcmc_samples) # above 1.1 indicates a lack of convergence
#saveRDS(gelman_diag, file = "gelman_diag.rds") # read in with gelman_diag <- readRDS("gelman_diag.rds")

# Multivariate mpsrf:
(gelman_diag$mpsrf)

# Get PSRFs
psrf_values <- as.data.frame(gelman_diag$psrf) #gelman.diag(mcmc_samples)$psrf
# Save the dataframe to a CSV file
write.csv(psrf_values, "psrf_values.csv", row.names = TRUE)

# Barplot
barplot(psrf_values$`Point est.`, main = "Potential Scale Reduction Factors \n (x-axis labels only show a subset of parameters due to plot size)", names.arg = rownames(psrf_values),las = 2)

# Show those above 1.1
psrf_values_above1.1 <- psrf_values %>% filter(`Point est.`>1.1) # n = 2

# Show those above 1.05
psrf_values_above1.05 <- psrf_values %>% filter(`Point est.`>1.05) # n = 6
```

```{r auto_correlation}
# --- Checking autocorrelation
#autocorr.diag(mcmc_samples) # takes very, very long
library(coda)
autocorr_results <- coda::autocorr(mcmc_samples, lags = 1)
#saveRDS(autocorr_results, file = "autocorr_results.rds") 

# Check class
class(autocorr_results)

# Extract just the diagonal (each vector contains the autocorrelation at lag 1 for each parameter)
autocorr_diag <- lapply(autocorr_results, function(x) diag(x[,,1]))

# Do a summary for each
summary(as.numeric(autocorr_diag[[1]]))
summary(as.numeric(autocorr_diag[[2]]))
summary(as.numeric(autocorr_diag[[3]]))

# Autocorr_diag is a list of vectors, where each vector contains autocorrelation at lag 1 for each parameter. We can plot with barplots:
par(mfrow = c(3, 1))

# Now plot each autocorrelation bar plot with turquoise color; they will be arranged into the grid automatically
barplot(autocorr_diag[[1]], main="Autocorrelation at lag 1, chain 1", xlab="Parameter Index", ylab="Autocorrelation", col="turquoise")
barplot(autocorr_diag[[2]], main="Autocorrelation at lag 1, chain 2", xlab="Parameter Index", ylab="Autocorrelation", col="turquoise")
barplot(autocorr_diag[[3]], main="Autocorrelation at lag 1, chain 3", xlab="Parameter Index", ylab="Autocorrelation", col="turquoise")

# Reset the plotting layout to default
par(mfrow = c(1, 1))

```

```{r inspect_autocorr}
# Defining a threshold for outliers
threshold <- 0.2

# Find indices where autocorrelation exceeds the threshold in absolute value for the first chain
outliers_chain1 <- which(abs(autocorr_diag[[1]]) > threshold)

# Repeat for the second and third chains
outliers_chain2 <- which(abs(autocorr_diag[[2]]) > threshold)
outliers_chain3 <- which(abs(autocorr_diag[[3]]) > threshold)

# Find outliers that are common across all chains
common_outliers <- Reduce(intersect, list(outliers_chain1, outliers_chain2, outliers_chain3))

# Retrieve the parameter names for the common outliers using the varnames function
parameter_names <- varnames(mcmc_samples)
common_outlier_names <- parameter_names[common_outliers]
```

```{r ESS}
# Run ESS
effective_size_results <- coda::effectiveSize(mcmc_samples)

# Get summary
summary(effective_size_results)

# Make df to inspect
effective_size_results_df <- data.frame(effective_size_results)

# Make barplot
barplot(effective_size_results, main = "Effective Sample Sizes \n (x-axis only shows subset of varnames because of the size)", names.arg = names(effective_size_results), las=2)
```

```{r traceplots}
library(bayesplot)

# Get param names
parameter_names <- varnames(mcmc_samples)
length(parameter_names)

# Select the parameter with the highest PSRF for rho, omega, and alpha
rho_params <- rownames(psrf_values)[grepl("rho", rownames(psrf_values))]
omega_params <- rownames(psrf_values)[grepl("omega", rownames(psrf_values))]
alpha_params <- rownames(psrf_values)[grepl("alpha", rownames(psrf_values))]

# Find the top three parameters with the highest PSRF values in each group
top3_psrf_alpha <- alpha_params[order(psrf_values[alpha_params, "Point est."], decreasing = TRUE)[1:3]]
top3_psrf_rho <- rho_params[order(psrf_values[rho_params, "Point est."], decreasing = TRUE)[1:3]]
top3_psrf_omega <- omega_params[order(psrf_values[omega_params, "Point est."], decreasing = TRUE)[1:3]]

# Filter parameters where point estimates are lower than 1.1
rho_params_under_1_1 <- rho_params[psrf_values[rho_params, "Point est."] < 1.1]
omega_params_under_1_1 <- omega_params[psrf_values[omega_params, "Point est."] < 1.1]
alpha_params_under_1_1 <- alpha_params[psrf_values[alpha_params, "Point est."] < 1.1]

# Sample one random parameter from each list
random_rho <- sample(rho_params_under_1_1, 1)
random_omega <- sample(omega_params_under_1_1, 1)
random_alpha <- sample(alpha_params_under_1_1, 1)

# Combine the random samples into one vector
random_traces <- c(random_alpha, random_rho, random_omega)

# 
# Make plots
library(bayesplot)
library(gridExtra)
library(ggplot2)

turquoise_colors <- c("darkslategray2", "darkslategray3", "darkslategray4")

# Function to create individual trace plots
create_trace_plot <- function(parameter) {
  bayesplot::mcmc_trace(mcmc_samples, pars = parameter) +
    labs(title = paste("Trace for", parameter),
         subtitle = paste("PSRF:", psrf_values[parameter, "Point est."])) +
    theme(plot.title = element_text(face = "bold"),
          plot.subtitle = element_text(face = "plain")) +
    scale_color_manual(values = turquoise_colors)
}


# Generate plots for alpha
plots_alpha <- lapply(top3_psrf_alpha, create_trace_plot)

# Generate plots for rho
plots_rho <- lapply(top3_psrf_rho, create_trace_plot)

# Generate plots for omega
plots_omega <- lapply(top3_psrf_omega, create_trace_plot)

# Generate plots for random
plots_random <- lapply(random_traces, create_trace_plot)

# Combine all plots into a 3x3 grid
grid.arrange(grobs = c(plots_alpha, plots_rho, plots_omega,plots_random), nrow = 4, ncol = 3)

```

```{r}
parameter_names <- varnames(mcmc_samples)
print(parameter_names)
length(parameter_names)  # Gives you the count of parameters
```

# 4. Preprocess for lm()
We need to make a subject-lookup table to get the ids and match them with the right values.

## Subject lookup table [RUN POST-FIT OF SAMPLES]
```{r subj_lookup}
# Extract the relevant columns from DMdata
subject_lookup <- DMdata[, c("id", "group_subjectid", "idgroup", "type", "grouptype", "condition")]

# Remove duplicate rows
subject_lookup <- unique(subject_lookup)

# Apply the idgroup mapping to convert idgroup values to sequential indices
subject_lookup$idgroup_mapped <- idgroup_mapping[as.character(subject_lookup$idgroup)]

# Arrange the lookup table (optional, for easier readability)
subject_lookup <- subject_lookup[order(subject_lookup$idgroup_mapped, subject_lookup$group_subjectid),]

# View the first few rows of the lookup table
head(subject_lookup)

# ---- Get their original id from the lookup when pulling out rho
# Initialize a dataframe to store the results
rho_values_df <- data.frame(
  original_id = integer(), 
  rho_mode = numeric(), 
  matrix_position = character()
)

# Loop over each combination of group_subjectid and idgroup
for (g in seq_len(ngroups)) {
    for (s in seq_len(groupSize)) {
        
      # Get the original subject ID
        original_id <- subset(subject_lookup, idgroup_mapped == g & group_subjectid == s)$id
        
        # Extract the rho values for this subject
        rho_values <- samples$BUGSoutput$sims.list$rho[, s, g]
        
        # Compute the mode of the rho values
        rho_mode <- MPD(rho_values)

        # Create a string representation of the matrix position
        matrix_pos <- paste("(", s, ",", g, ")", sep = "")

        # Combine the original ID, rho mode, and matrix position
        rho_values_df <- rbind(rho_values_df, data.frame(
          original_id = original_id, 
          rho_mode = rho_mode, 
          matrix_position = matrix_pos
        ))
    }
}

head(rho_values_df)
```

```{r make_lms}
# Initialize a dataframe to store results
results <- data.frame(id = unique(contributions$id), 
                      beta_slope = numeric(length(unique(contributions$id))),
                      adj_r2 = numeric(length(unique(contributions$id))))

# Initialize a list to store model summaries
model_summaries <- list()

# Initialize a list to store residual plots
residual_plots <- list()

# Initialize a list to store Q-Q plots
qq_plots <- list()

# Loop through each unique ID
for (i in seq_along(results$id)) {
    # Filter data for the current ID
    filtered_data <- contributions %>% filter(id == results$id[i])
    
    # Fit the model without an intercept
    model <- lm(preferred_contribution ~ avg_group_contr + 0, data = filtered_data)
    
    # Store the slope in the results dataframe
    results$beta_slope[i] <- coef(model)["avg_group_contr"]
    results$adj_r2[i] <- summary(model)$adj.r.squared
    
    # Replace NA or NaN in adj_r2 with 0
    if (is.na(results$adj_r2[i]) || is.nan(results$adj_r2[i])) {
            results$adj_r2[i] <- 0
    }
    
    # Store the summary of the model in the list
    model_summaries[[as.character(results$id[i])]] <- summary(model)
    
    # Calculate residuals for the current model
    #model_residuals <- residuals(model)
    # Create a data frame with residuals
    residuals_df <- data.frame(residuals = residuals(model))
    
    # Generate and store the Q-Q plot
    p <- ggplot(residuals_df, aes(sample = residuals)) +
         stat_qq() +
         stat_qq_line(col = "red") +
         labs(title = paste("Q-Q Plot for Residuals of ID", results$id[i]),
              x = "Theoretical Quantiles",
              y = "Sample Quantiles")

    qq_plots[[i]] <- p
    # # Generate a residual plot for the current model
    # p <- ggplot(filtered_data, aes_string(x = "avg_group_contr", y = residuals(model))) +
    #      geom_point() +
    #      geom_hline(yintercept = 0, linetype = "dashed") +
    #      labs(title = paste("Residual Plot for ID", results$id[i]),
    #           x = "Average Group Contribution",
    #           y = "Residuals")
    # residual_plots[[i]] <- p
    
    #  # Generate a Q-Q plot for the current model's residuals
    # p <- ggplot2::ggplot() +
    #      ggplot2::geom_qq(aes(sample = model_residuals)) +
    #      ggplot2::geom_qq_line(aes(sample = model_residuals), col = "red") +
    #      ggplot2::labs(title = paste("Q-Q Plot for Residuals of ID", results$id[i]),
    #                    x = "Theoretical Quantiles",
    #                    y = "Sample Quantiles")
    # 
    # # Add the plot to the list
    # qq_plots[[i]] <- p
}

# A lot of them have zeros.Inspecting:
summary(lm(preferred_contribution ~ avg_group_contr + 0, data = contributions %>% filter(id == 7)))
#results_zeros <- results %>% filter(beta_slope == 0)
#length(unique(results_zeros$id))
print(results)

```

```{r}
# Plot beta slope with R^2
results <- merge(contributions,results, by = "id")

# 'type' and 'grouptype' are columns in rho_and_beta dataframe
results %>% ggplot(aes(x = adj_r2, y = beta_slope, color = type)) +
  geom_point() +
  #geom_abline(slope = 1, intercept = 0, color = "blue", linetype = "dashed") +
  theme_minimal() +
  labs(
    title = "Scatter Plot of adj_r2 vs. beta_slope from contribution table models",
    subtitle = "Point in 0,0 is 39 players who constantly gave 0 in the contribution table \n (perfect freeriders)",
    x = "adj_r2",
    y = "beta_slope"
  ) +
  scale_color_brewer(palette = "Set1") +
  scale_shape_manual(values = c(16, 17, 18, 19, 20))
```

```{r merging}

# ---------- now we have two dataframes: 
results # the lm results for each id
rho_values_df # the rho values for each id

# MERGE TO HAVE BOTH RHO AND BETA
rho_and_beta <- merge(results,
                     rho_values_df,
                     by.x = "id",
                     by.y = "original_id") %>%
  
                      rename(#beta_slope = slope,
                             rho_mode_from_jags = rho_mode)
# Make beta_slope_norm01
rho_and_beta <- rho_and_beta %>% 
  mutate(beta_slope_norm01 = (beta_slope - min(beta_slope)) / (max(beta_slope) - min(beta_slope)))

# Get grouptypes on
grouptypes_id <- DMdata %>%
  select(grouptype, id) %>%
  distinct(id, .keep_all = TRUE)

# Merge it on
rho_and_beta <- merge(rho_and_beta,grouptypes_id, by = 'id')

# Inspect
colnames(rho_and_beta)
head(rho_and_beta)

# Plotting densities for inspection
plot(density(rho_and_beta$rho_mode_from_jags))
plot(hist(rho_and_beta$rho_mode_from_jags))

plot(density(rho_and_beta$beta_slope_norm01))
plot(hist(rho_and_beta$beta_slope_norm01))
```

# 5. Correlation Analysis
```{r}
# Reduce dataset to only have one
rho_and_beta_192 <- rho_and_beta %>%
                    select(id, 
                           beta_slope, 
                           beta_slope_norm01, 
                           rho_mode_from_jags) %>% filter(!duplicated(id))

# Looking at subject nr 7 (freerider, but with near perfect CC behaviour)
rho_and_beta_test <- rho_and_beta %>% filter(id == 7)
DMdata_test <- DMdata %>% filter(id == 7)

# Variables to use
rho_and_beta_192$beta_slope_norm01
rho_and_beta_192$rho_mode_from_jags

# -- Checking normality
library(pastecs)

# - Beta slopes
stat.desc(rho_and_beta_192$beta_slope_norm01, basic = TRUE, desc = TRUE, norm = TRUE, p = 0.95) # not normal
hist(rho_and_beta_192$beta_slope_norm01)
qqnorm(rho_and_beta_192$beta_slope_norm01)
qqline(rho_and_beta_192$beta_slope_norm01)

# - Rhos
stat.desc(rho_and_beta_192$rho_mode_from_jags, basic = TRUE, desc = TRUE, norm = TRUE, p = 0.95) # not normal
hist(rho_and_beta_192$rho_mode_from_jags)
qqnorm(rho_and_beta_192$rho_mode_from_jags)
qqline(rho_and_beta_192$rho_mode_from_jags)

# -- Checking ranks
sum(table(rho_and_beta_192$beta_slope_norm01) > 1)
sum(table(rho_and_beta_192$rho_mode_from_jags) > 1)

# -- Investigating monotonic relationship
plot(rho_and_beta_192$beta_slope_norm01, rho_and_beta_192$rho_mode_from_jags, main = "Scatterplot", xlab = "beta-slopes-norm01", ylab = "Rhos from Jags", pch = 19)

```

```{r}
# Spearman's Rho
cor_test_result <- cor.test(rho_and_beta_192$beta_slope_norm01, rho_and_beta_192$rho_mode_from_jags, method = "spearman")
cor_test_result

# Get type vars on
DMdata_vars <- DMdata %>% select(id,
                                 type,
                                 grouptype,
                                 bin_strategic_ability,
                                 group_ability_cont,
                                 group_ability_cat) %>% filter(!duplicated(id))

rho_and_beta_192_ <- merge(rho_and_beta_192, DMdata_vars, by = 'id')

# Custom color palette
turquoise_palette <- c("darkslategray1", "darkslategray", "darkslategray4", "darkturquoise")
red_palette <- c("red", "darkred", "maroon", "chocolate")

# Plot 1: Color by 'type'
plot1 <- rho_and_beta_192_ %>%
  ggplot(aes(x = beta_slope_norm01, y = rho_mode_from_jags, color = type)) +
  geom_point() +
  geom_abline(slope = 1, intercept = 0, color = "black", linetype = "dashed") +
  theme_minimal() +
  labs(
    #title = "Beta-slopes (stated preferences) vs. \nRhos (readiness to cooperate)",
    subtitle = "Coloring for preference type (as per contribution tables).",
    x = "Beta-slope (from contribution table)",
    y = "MPD of rho post. per subject (from JAGS model)"
  ) +
  scale_color_manual(values = turquoise_palette) +
  theme(plot.title = element_text(face = "bold"))

# Plot 2: Shape by 'grouptype'
plot2 <- rho_and_beta_192_ %>%
  ggplot(aes(x = beta_slope_norm01, y = rho_mode_from_jags, color = grouptype)) +
  geom_point() +
  geom_abline(slope = 1, intercept = 0, color = "black", linetype = "dashed") +
  theme_minimal() +
  labs(
    #title = "Beta-slopes (stated preferences) vs. \nRhos (readiness to cooperate)",
    subtitle = "Color for grouptype.",
    x = "Beta-slope (from contribution table)",
    #y = "MPD of rho per subject (from JAGS model)"
    y = NULL
  ) +
  #scale_shape_manual(values = c(16, 17, 18, 19)) +
  scale_color_manual(values = red_palette) +
  theme(plot.title = element_text(face = "bold"))

# Combine the two plots in a grid with one common title
library(grid)
grid.arrange(
  plot1, plot2,
  nrow = 1,
  top = textGrob("Beta-slopes (stated preferences) vs. inferred rhos (readiness to cooperate)",
                 gp = gpar(fontface = "bold", fontsize = 14))
)

```

# 6. Post-hoc part A
```{r}
# Spearman's Rho using non-normalised Betas
cor_test_result <- cor.test(rho_and_beta_192$beta_slope, rho_and_beta_192$rho_mode_from_jags, method = "spearman")
cor_test_result

# Kendall's tau using non-normalised Betas
cor_test_result <- cor.test(rho_and_beta_192$beta_slope, rho_and_beta_192$rho_mode_from_jags, method = "kendall")
cor_test_result

# Kendall's tau using normalised Betas
cor_test_result <- cor.test(rho_and_beta_192$beta_slope_norm01, rho_and_beta_192$rho_mode_from_jags, method = "kendall")
cor_test_result

```

```{r}
 
both_slopes_with_original_ids <- both_slopes_with_original_ids %>% rename(original_id = id_proper)
rho_and_beta_all <- merge(both_slopes_with_original_ids, rho_and_beta, by = "original_id")

# COR TEST
# - Seeing whether their actual behaviour from the game (as per an lmer() correlated with the beta_slope from their contribtuion tables)
cor_test_result <- cor.test(rho_and_beta_all$beta_slope, rho_and_beta_all$slope.x, method = "kendall")
cor_test_result 

# - Seeing whether slope from game behavioru and rho from game behavioru correlate
cor_test_result <- cor.test(rho_and_beta_all$rho_mode_from_jags, rho_and_beta_all$slope.x, method = "kendall")
cor_test_result 

# - Seeing whether their contribution table beta correlates with rho from cog models
cor_test_result <- cor.test(rho_and_beta_all$rho_mode_from_jags, rho_and_beta_all$beta_slope, method = "kendall")
cor_test_result 

```

# 7. Post-hoc part B: do lm()s for actual in-game contributions
```{r}
ingame_contributions <- DMdata %>% select(id,
                                          idgroup,
                                          type,
                                          period,
                                          contribution_id,
                                          avg_contr_g_others)


# Initialize a dataframe to store results
results_ingame_contributions <- data.frame(id = unique(ingame_contributions$id), 
                                           beta_slope_ingame = numeric(length(unique(ingame_contributions$id))),
                                           adj_r2_ingame = numeric(length(unique(ingame_contributions$id))))

# Initialize a list to store model summaries
model_summaries <- list()

# Loop through each unique ID
for (i in seq_along(results_ingame_contributions$id)) {
    # Filter data for the current ID
    filtered_data <- ingame_contributions %>% filter(id == results_ingame_contributions$id[i])
    
    # Fit the model without an intercept
    model <- lm(contribution_id ~ avg_contr_g_others, data = filtered_data)
    
    # Store the slope in the results dataframe
    results_ingame_contributions$beta_slope_ingame[i] <- coef(model)["avg_contr_g_others"]
    results_ingame_contributions$adj_r2_ingame[i] <- summary(model)$adj.r.squared
    
    # Replace NA or NaN in adj_r2 with 0
    if (is.na(results_ingame_contributions$adj_r2_ingame[i]) || is.nan(results_ingame_contributions$adj_r2_ingame[i])) {
            results_ingame_contributions$adj_r2_ingame[i] <- 0
    }
    
    # Store the summary of the model in the list
    model_summaries[[as.character(results_ingame_contributions$id[i])]] <- summary(model)
    
}

# Make beta_slope_norm01
results_ingame_contributions <- results_ingame_contributions %>% 
  mutate(beta_slope_ingame_norm01 = (beta_slope_ingame - min(beta_slope_ingame)) / (max(beta_slope_ingame) - min(beta_slope_ingame)))



### Make it for no intercept models
# Initialize a dataframe to store results
results_ingame_contributions_no_int <- data.frame(id = unique(ingame_contributions$id), 
                                           beta_slope_ingame_no_int = numeric(length(unique(ingame_contributions$id))),
                                           adj_r2_ingame_no_int = numeric(length(unique(ingame_contributions$id))))

# Initialize a list to store model summaries
model_summaries <- list()

# Loop through each unique ID
for (i in seq_along(results_ingame_contributions_no_int$id)) {
    # Filter data for the current ID
    filtered_data <- ingame_contributions %>% filter(id == results_ingame_contributions_no_int$id[i])
    
    # Fit the model without an intercept
    model <- lm(contribution_id ~ avg_contr_g_others + 0, data = filtered_data)
    
    # Store the slope in the results dataframe
    results_ingame_contributions_no_int$beta_slope_ingame_no_int[i] <- coef(model)["avg_contr_g_others"]
    results_ingame_contributions_no_int$adj_r2_ingame_no_int[i] <- summary(model)$adj.r.squared
    
    # Replace NA or NaN in adj_r2 with 0
    if (is.na(results_ingame_contributions_no_int$adj_r2_ingame_no_int[i]) || is.nan(results_ingame_contributions_no_int$adj_r2_ingame_no_int[i])) {
            results_ingame_contributions_no_int$adj_r2_ingame_no_int[i] <- 0
    }
    
    # Store the summary of the model in the list
    model_summaries[[as.character(results_ingame_contributions_no_int$id[i])]] <- summary(model)
    
}

# Make beta_slope_norm01
results_ingame_contributions_no_int <- results_ingame_contributions_no_int %>% 
  mutate(beta_slope_ingame_no_int_norm01 = (beta_slope_ingame_no_int - min(beta_slope_ingame_no_int)) / (max(beta_slope_ingame_no_int) - min(beta_slope_ingame_no_int)))

# --- Merge the two results dataframes
results_ingame_contributions_ <- merge(results_ingame_contributions,results_ingame_contributions_no_int, by = "id")

# Merge on
rho_and_beta_192__ <- merge(rho_and_beta_192,results_ingame_contributions_, by = "id")

```

```{r correlate_w_posthoc}
# Correlate
# - Main corr analysis
cor_test_main <- cor.test(rho_and_beta_192__$beta_slope_norm01, rho_and_beta_192__$rho_mode_from_jags, method = "spearman")
cor_test_main

# - Posthoc corr1: beta_slope_norm01 vs beta_slope_ingame_norm01 (no int)
cor_test_ph1 <- cor.test(rho_and_beta_192__$beta_slope_norm01, rho_and_beta_192__$beta_slope_ingame_no_int_norm01, method = "spearman")
cor_test_ph1 # With an intercept, the correlation decreases and p-value increases

# - Posthoc corr2: beta_slope vs beta_slope_ingame (not normalised)
cor_test_ph2 <- cor.test(rho_and_beta_192__$beta_slope, rho_and_beta_192__$beta_slope_ingame_no_int, method = "spearman")
cor_test_ph2 # largely same as cor_test_ph1

# - Posthoc corr3: beta_slope_ingame_norm01 vs rho
cor_test_ph3 <- cor.test(rho_and_beta_192__$beta_slope_ingame_no_int_norm01, rho_and_beta_192__$rho_mode_from_jags, method = "spearman")
cor_test_ph3 # strong correlation

```
